Making Sequential Programs Deterministic

### 2019-03-22 design.tex
More tweaks

\begin{itemize}
	\item Set.equals() is annotated as \<@Poly("up")>. This is sound but imprecise.
	\item Example1: \codeid{@OrderNonDet Set<@Det List>.equals(@OrderNonDet Set<@Det List>)} is deterministic
	\item Example2: \codeid{@OrderNonDet Set<@OrderNonDet List>.equals(@OrderNonDet Set<@OrderNonDet List>)} is not deterministic.
	\item Explain the rules under which we make Set equality deterministic.
	\item We annotate System.getProperty as \<@NonDet> because the results could vary across machines.
	\item Exceptions: line.Sepaator, file.Separator. and path.Separator.
\end{itemize}

@@

\begin{itemize}
	\item A map is deterministic if the keySet() is deterministic.
	\item the iteration order of a keyset is the same as the iteration order of entrySet and Values.
	\item \<HashMap> - can be \<@OrderNonDet> or \<@NonDet>.
	\item \<LinkedHashMap> - can be \<@Det>, \<@OrderNonDet>, ot \<@NonDet>.
	\item \<TreeMap> - can be \<@Det> or \<@NonDet>.
	\item Problem with \<Map.get()> : Annotating as \<@PolyDet> is imprecise.
	\item We circumvent this by hardcoding rules to make it precise. (Describe the rule here)
	\item It was probably a bad design choice to make HashMap a subclass of Map (talk about how
	every method is overriden). Similarly for HashSet.
\end{itemize}

>>>>

\begin{itemize}
	\item \<Set.equals()> is annotated as \<@Poly("up")>. This is sound but imprecise.
	\item Example1: \codeid{@OrderNonDet Set<@Det List>.equals(@OrderNonDet Set<@Det List>)} is deterministic
	\item Example2: \codeid{@OrderNonDet Set<@OrderNonDet List>.equals(@OrderNonDet Set<@OrderNonDet List>)} is not deterministic.
	\item Explain the rules under which we make Set equality deterministic.
	\item We annotate System.getProperty as \<@NonDet> because the results could vary across machines.
	\item Exceptions: line.Sepaator, file.Separator. and path.Separator.
\end{itemize}

@@

\begin{itemize}
	\item A map is deterministic iff the \<entrySet()> is
          deterministic; equivalently, iff the \<keySet()> and \<values()>
          are both deterministic
	\item the iteration order of a keyset is the same as the iteration order of entrySet and Values.
	\item \<HashMap> - can be \<@OrderNonDet> or \<@NonDet>.
	\item \<LinkedHashMap> - can be \<@Det>, \<@OrderNonDet>, ot \<@NonDet>.
	\item \<TreeMap> - can be \<@Det> or \<@NonDet>.
	\item Problem with \<Map.get()> : Annotating as \<@PolyDet> is imprecise.
	\item We circumvent this by hardcoding rules to make it precise. (Describe the rule here)
	\item It was probably a bad design choice to make HashMap a subclass of Map (talk about how
	every method is overriden). Similarly for HashSet.
\end{itemize}
